Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-03-15 analysis/paper/paper.Rmd
Add more description to data analysis

The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production. Various countries, e.g., Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [@MOEF2015]. However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.

@@

Data were analysed using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2017].

@@

# Conclusions (optional)

>>>>

The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production. Various countries, \textit{e.g.}, Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [@MOEF2015]. However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.

@@

Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill. Five and four disease assessments were made in 2015 and 2016, respectively. Data were analysed using the area under the disease progress stairs (AUDPS) and multivariate generalised linear mixed models. We were unable to detect any differences in disease in either experiment due to irrigation methods, N rates or the interaction of the two treatments in either season. Our findings indicate that farmers can safely adopt the AWD technology without risk of increasing sheath blight disease.

Disease severity was converted to area under the disease progress stairs (AUDPS) [@simko2012area] and analysed using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2017].

@@
